### 2019-11-22 thesis/content/chapter-related-work.tex
minor fixes

\paragraph{Graph embeddings}
Skip-gram methods can not only be used for vertex embeddings but also to embed entire graphs.
One way to do this is via the \texttt{graph2vec}~\cite{Narayanan2017} method.
It is inspired by \texttt{doc2vec}~\cite{Le2014} which in turn is based on \texttt{word2vec}.
\texttt{graph2vec} gets a set of graphs $\mathbb{G} = \{ G_1, \dots G_N \}$ as input and outputs graph embeddings $f(G_1), \dots, f(G_N)$.
While in \texttt{word2vec} every word can be a context root as well as a context element, \texttt{graph2vec} uses the graphs $\mathbb{G}$ as context roots.
The context $C_k(G_i)$ of a graph $G_i = (\mathcal{V}_i, \mathcal{E}_i)$ is defined as
\begin{equation}
	C_k(G_i) := \bigcup_{\mathclap{v_j \in \mathcal{V}_i}}\, {\left\{ {\textrm{WL}_l(G_i)}_j \right\}}_{l = 0}^k % chktex 21
	\text{ with } \textrm{WL}_l(G) := \text{\acs{wl} colors after $l$ iter.\ on $G$.}
\end{equation}
Intuitively this context can be understood as the set of isomorphically distinct subgraphs of $G_i$ with diameter $\leq 2k$.
Since \ac{wl} is used to identify isomorphic subgraphs, \texttt{graph2vec} can only be applied to graphs with discrete vertex labels.
Using the previous definitions, the context root embedding function has the signature $f: \mathbb{G} \to \mathbb{R}^d$ while the context element embedding function is of type $f_C: \bigcup_{G_i \in \mathbb{G}} C_k(G_i) \to \mathbb{R}^d$.
To find those embeddings the \texttt{word2vec} objective from \cref{eq:related:gcr:embed:word2vec} is reused.
Analogous to \texttt{word2vec}, \texttt{graph2vec} therefore embeds graphs that share isomorphic subgraphs close to each other, whereas graphs that do not share substructures tend to be embedded further away from each other.

@@

>>>>

\paragraph{Graph embeddings}
Skip-gram methods can not only be used for vertex embeddings but also to embed entire graphs.
One way to do this is via the \texttt{graph2vec}~\cite{Narayanan2017} method.
It is inspired by \texttt{doc2vec}~\cite{Le2014} which in turn is based on \texttt{word2vec}.
\texttt{graph2vec} gets a set of graphs $\mathbb{G} = \{ G_1, \dots G_N \}$ as input and outputs graph embeddings $f(G_1), \dots, f(G_N)$.
While in \texttt{word2vec} every word can be a context root as well as a context element, \texttt{graph2vec} uses the graphs $\mathbb{G}$ as context roots.
The context $C_k(G_i)$ of a graph $G_i = (\mathcal{V}_i, \mathcal{E}_i)$ is defined as
\begin{equation}
	C_k(G_i) := \bigcup_{\mathclap{v_j \in \mathcal{V}_i}}\, {\left\{ {\textrm{WL}_l(G_i)}_j \right\}}_{l = 0}^k % chktex 21
	\text{ with } \textrm{WL}_l(G) := \text{\acs{wl} colors after $l$ iter.\ on $G$.}
\end{equation}
Intuitively this context can be understood as the set of \acs{wl}-distinguishable subgraphs of $G_i$ with diameter $\leq 2k$.
Since \ac{wl} is used to identify distinct subgraphs, \texttt{graph2vec} can only be applied to graphs with discrete vertex labels.
Using the previous definitions, the context root embedding function has the signature $f: \mathbb{G} \to \mathbb{R}^d$ while the context element embedding function is of type $f_C: \bigcup_{G_i \in \mathbb{G}} C_k(G_i) \to \mathbb{R}^d$.
To find those embeddings the \texttt{word2vec} objective from \cref{eq:related:gcr:embed:word2vec} is reused.
Analogous to \texttt{word2vec}, \texttt{graph2vec} therefore embeds graphs that share subgraphs close to each other, whereas graphs that do not share substructures tend to be embedded further away from each other.

@@

Instead of explicity mapping a graph or vertices into a vector space, one can also do so implicity by employing the kernel trick.
There is a large variety of so-called \acp{gk} to do this.
\acp{gk} can be used in combination with any kernel method to solve the \ac{gcr} problem.
